\documentclass{resume}

% --- Customization to change section headers from all caps ---
\usepackage{etoolbox}
\patchcmd{\leftsectionformat}{\textbf{#1}}{\textbf{\MakeUppercase #1}}{}{} % Revert uppercase for left sections
\patchcmd{\section}{\bfseries}{\bfseries\MakeUppercase}{}{} % Revert uppercase for right sections

\renewcommand{\leftsectionformat}[1]{%
	\vspace{0.7em}%
	{{\ResumeHeadingSize\textbf{#1}}}%
	\vspace{0.3em}\par%
}

\titleformat{\section}{\ResumeHeadingSize\bfseries}{}{0em}{}
% --- End Customization ---


\begin{document}

% --------------------
%       HEADER
% --------------------
\resumename{Hamza Kamal}
\resumeinfo{
	\infoitem{425 500 8240} \infosep
	\infoitem{kamal.hamza@outlook.com} \infosep
	\infoitem{Sammamish, WA}
}

% --------------------
%       BODY
% --------------------
\begin{resume}

	% --------------------
	%    LEFT COLUMN
	% --------------------

	\begin{skillssection}
		\skillcategory{Technical}{Python, JavaScript, C\#, Java, C++, SQLite, HTML, CSS, Django, React, PyGame, Firebase, Langchain, Bootstrap, Open Street Maps, OpenAI, Ollama, Azure AI Foundry, Azure AI Search, Azure Blob Storage, Azure SQL DB, Azure DevOps, Azure App Service, YAML}
		\skillcategory{Soft}{Leadership, Problem-Solving, Communication, Agile Methodologies, Sprint Planning, Stand-up Meetings}
	\end{skillssection}
	\begin{educations}
		\educationentry{University of Washington, Bothell, WA}{Bachelor's in Computer Science and Software Engineering}{Sep 2023 - Current}
	\end{educations}

	\begin{coursessection}
		\courseentry{Data Structures and Algorithms}
		\courseentry{Analysis and Design}
		\courseentry{Hardware and Computer Organization}
		\courseentry{Operating Systems}
		\courseentry{Intro to AI}
	\end{coursessection}

	\begin{linkssection}
		\linkentry{\textbf{GitHub:} github.com/kamal-hamza}
		\linkentry{\textbf{LinkedIn:} linkedin.com/in/kamal-hamza/}
	\end{linkssection}


	% --------------------
	%    RIGHT COLUMN
	% --------------------

	\begin{experiences}
		\experienceentry{Software Engineer Intern}{June 2025 - August 2025}{Quadrant Technologies}{}
		{
			\item Built a Job Recommendation AI Feature with Azure AI tools, improving accuracy from inconsistent results to 100\% in manual testing.
			\item Developed and optimized 5+ build/release pipelines in Azure DevOps, reducing deployment time by 40\%.
			\item Developed 20+ backend API endpoints in Django to expand web app features.
			\item Deployed the site on Azure App Service for 500+ employees.
			\item Enhanced HR Portal and Recruitment Services in React, increasing user satisfaction by 60\%.
		}
		\experienceentry{Software Developer - .NET Framework to .NET Core}{December 2024 - June 2025}{Fraser River Software}{}
		{
			\item Migrated legacy ASP.NET app to .NET Core 8.0, boosting performance and compatibility.
			\item Refactored codebase using modern .NET Core practices like dependency injection.
			\item Performed comprehensive testing and debugging to ensure post-migration stability.
		}
		\experienceentry{Team Lead for MAPS Hackathon}{August 2024}{Muslim Association of Puget Sound}{}
		{
			\item Led development of a room reservation app, spearheading the frontend with React and Firebase.
			\item Managed team tasks and communication to ensure effective collaboration.
		}
	\end{experiences}

	\begin{projects}
		\projectentry{Unix-like File System}{}
		{ \item Built a Unix-like file system in C with hierarchical directories, file metadata, and efficient storage.
			\item Developed custom read/write and directory traversal functions to simulate core OS file operations.
			\item \textbf{Technologies used:} C.
		}
		\projectentry{Review Website}{}
		{
			\item Created a product review site with user authentication, CRUD operations, and AI-powered summary generation.
			\item \textbf{Technologies used:} JavaScript, HTML, CSS, React, Django, Langchain, Bootstrap, Ollama.
		}
	\end{projects}

\end{resume}
\end{document}
